---
title: "chemical_mixture"
author: "yuqimiao"
date: "2021-01-08"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---

## This web is to explore a new analysis methods for the association between chemical mixture and health outcome

```{r}
library(bkmr)
library(wqs)
library(tidyverse)
```

# scenario 1: 2 components with interaction in a non-linear form, independent

## BKMR method implementation
```{r}
scenario1 = SimData(n = 100, M = 5)
y = scenario1$y
Z = scenario1$Z
X = scenario1$X
set.seed(111)

## record the time taken
start.time <- Sys.time()
fitkm <- kmbayes(y = y, Z = Z, X = X, iter = 10000, verbose = FALSE, varsel = TRUE)
end.time <- Sys.time()
time.taken1 <- end.time - start.time
time.taken1

## calculate PIPs 
ExtractPIPs(fitkm)

## value of r and delta
par(mfrow = c(4,1))
for(i in 1:4){
  TracePlot(fitkm, par = "r", comp  = i)
}

colMeans(fitkm$delta[5000:10000,])

```

## WQS implementation

```{r}
start.time <- Sys.time()
fitwqs = wqs.est(y.train = y,x.train = Z,z.train = X)
end.time <- Sys.time()
time.taken2 <- end.time - start.time
time.taken2

fitwqs$weights
```

# scenario 2: 2 components with interaction in a non-linear form, with 1st and 2nd correlated

## BKMR method implementation
```{r}
scenario2 = SimData(n = 100, M = 4, Zgen = "corr",sigsq.true = 2.2)
y = scenario2$y
Z = scenario2$Z
X = scenario2$X
round(cor(Z),2)
```


```{r}
## record the time taken
start.time <- Sys.time()
fitkm2 <- kmbayes(y = y, Z = Z, X = X, groups = c(1,2,1,3),  iter = 10000, verbose = FALSE, varsel = TRUE)
end.time <- Sys.time()
time.taken3 <- end.time - start.time
time.taken3

## calculate PIPs 
ExtractPIPs(fitkm2)

## value of r and delta
par(mfrow = c(4,1))
for(i in 1:4){
  TracePlot(fitkm, par = "r", comp  = i)
}

colMeans(fitkm$delta[5000:10000,])

```

## WQS implementation

```{r}
start.time <- Sys.time()
fitwqs2 = wqs.est(y.train = y,x.train = Z,z.train = X)
end.time <- Sys.time()
time.taken4 <- end.time - start.time
time.taken4

fitwqs2$weights
```


it can be seen that in scenario 2, where z1 and z3 are highly correlated. BKRM still performs well in this scenario, but why it can separate 2 variable is not clear to me. 
