---
title: "GL_SIMLR"
author: "yuqimiao"
date: "2020-10-06"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---

This is the exploration analysis page for the Global Local SIMLR algorithm

The main thoughts of the new algorithm is to using both the local and global information in weight optimization, the details is in Derivation/GL_SIMLR.pdf



```{r}
## package loading
library(tidyverse)
library(parallel)
library(clValid)
library(abSNF)
library(SNFtool)
library(igraph)
library(Matrix)
library(CancerSubtypes)

## mwe data
source("code/functions/simulation_function.R")
source("code/R/compute.multiple.kernel.R")
source("code/functions/simulation_verify.R")
source("./code/functions/gl_simlr.R")

```

# example usage

For the example run, using simulation scenario where the effective size are 2,3,5 respectively for 3 data types.
separating cluster 12/34,13/24,14/23 separately.

More scenario will be include in simulation

```{r}
set.seed(124)
sim = simulation_3(eff_size = c(2,3,5), sigma = rep(100,3))
data_list = list(data1 = standardNormalization(t(sim$data1)),
                 data2 = standardNormalization(t(sim$data2)),
                 data3 = standardNormalization(t(sim$data3)))
## GL_SIMLR_1 
gl_result = GL_SIMLR_1(data_list = data_list)
gl_result_3 = GL_SIMLR_4(data_list = data_list)


igraph::compare(gl_result$cluster,sim$truelabel,method = "rand")
igraph::compare(gl_result_3$cluster,sim$truelabel,method = "rand")
igraph::compare(gl_result$cluster,sim$truelabel,method = "nmi")
igraph::compare(gl_result_3$cluster,sim$truelabel,method = "nmi")

gl_result$w_list
gl_result_3$w_list
gl_result$cluster
gl_result_3$cluster

sort(desc(gl_result$converge),index.return = T)

gl_result_3$converge
gl_result$converge
```





# 1 term configuration

```{r}
## show the major contribution of weight from trace term
## one time, iteration compare the relationship between GL_trace and weight
par = list()
sub_ratio_ls = list(rep(1/4,4), c(0.1,0.2,0.3,0.4))
sample_size_ls = c(120,200)
eff_size_ls = list(c(1,1,1),c(1,3,3),c(1,3,5))
sigma_ls = c(1,10,100)
load("./data/configuration_data_40.Rdata")

g1 = as_tibble(W_g$GL_trace_all) %>% 
  mutate(ID = seq_along(V1)) %>% 
  pivot_longer(
    V1:V3,
    names_to = "data_type",
    values_to = "GL_trace"
  ) %>% 
  ggplot(aes(x = ID, y = GL_trace, color = data_type, group = data_type))+
  geom_line()+
  facet_grid(data_type~., scale = "free")

g2 = as_tibble(W_g$w_list_all) %>% 
  mutate(ID = seq_along(V1)) %>% 
  pivot_longer(
    V1:V3,
    names_to = "data_type",
    values_to = "weight"
  ) %>% 
  ggplot(aes(x = ID, y = weight, color = data_type, group = data_type))+
  geom_line()+
  facet_grid(data_type~., scale = "free")
library(patchwork)
g1+g2
```


```{r}
## load simulated data
eva_nmi = NULL
eva_rand = NULL
gl_weight = NULL
global_local = NULL
GL_trace = NULL
tunning_crit = NULL
gl_weight = NULL
tunning_best = NULL
files = list.files("./data/simu_1220/")
for(i in 1:length(files)){
  load(file = paste("./data/simu_1220/", files[i], sep = ""))
  eva_nmi = rbind(eva_nmi,res$eva_nmi)
  eva_rand = rbind(eva_rand, res$eva_rand)
  gl_weight = rbind(gl_weight, res$gl_weight)
  global_local = rbind(global_local, res$global_local)
  GL_trace = rbind(GL_trace,res$GL_trace)
  tunning_crit = rbind(tunning_crit, res$tunning_res)
  tunning_best = rbind(tunning_best, res$tunning_best)
  gl_weight = rbind(gl_weight, res$gl_weight)
}
# scenario_name = c(paste("n120", c(paste("eff111", paste("sig",sigma_ls, sep = ""),sep = "_"),
#                                      paste("eff133", paste("sig",sigma_ls, sep = ""),sep = "_"),
#                                      paste("eff135", paste("sig",sigma_ls, sep = ""),sep = "_")),
#                         sep = "_"),
#                   paste("n200", c(paste("eff111", paste("sig",sigma_ls, sep = ""),sep = "_"),
#                                      paste("eff133", paste("sig",sigma_ls, sep = ""),sep = "_"),
#                                      paste("eff135", paste("sig",sigma_ls, sep = ""),sep = "_")),
#                         sep = "_")
# )
# scenario_n = rep(scenario_name,100)

## show that no clear difference between with/without beta
eva_nmi %>% 
    # mutate(scenario = scenario_n) %>% 
    group_by(scenario) %>%
    summarise_all(mean)

eva_rand %>% 
  group_by(scenario) %>%
  summarise_all(mean)
  
eva_nmi %>% 
  group_by(scenario) %>%
  summarise_all(mean) %>% 
  pivot_longer(
    nmi_spec_s:nmi_spec_gt,
    names_to = "methods",
    values_to = "nmi"
  ) %>% 
  separate(scenario, into = c("size","eff_size","sigma"),sep = "_") %>% 
  ggplot(aes(x = eff_size, y = nmi, group = methods, color = methods))+
  geom_line(alpha = 0.5)+
  geom_point(alpha = 0.5)+
  facet_grid(size~sigma)

eva_rand  %>% 
  group_by(scenario) %>%
  summarise_all(mean) %>% 
  pivot_longer(
    rand_spec_c:rand_spec_gt,
    names_to = "methods",
    values_to = "rand"
  ) %>% 
  separate(scenario, into = c("size","eff_size","sigma"),sep = "_") %>% 
  ggplot(aes(x = eff_size, y = rand, group = methods, color = methods))+
  geom_line(alpha = 0.5)+
  geom_point(alpha = 0.5)+
  facet_grid(size~sigma)


eva_rand %>% 
  # mutate(scenario = scenario_n) %>% 
  dplyr::select(scenario = scenario, concatenate = rand_spec_c, MKL = rand_spec_g, snf = rand_spec_s) %>% 
  group_by(scenario) %>%
  summarise_all(mean) %>% 
  pivot_longer(
    concatenate:snf,
    names_to = "methods",
    values_to = "rand"
  ) %>% 
  separate(scenario, into = c("size","eff_size","sigma"),sep = "_") %>% 
  ggplot(aes(x = eff_size, y = rand, group = methods, color = methods))+
  geom_line(alpha = 0.5)+
  geom_point(alpha = 0.5)+
  facet_grid(size~sigma)
```


```{r}
### show the trivial distance between glocal and local term
global_local %>%
  # mutate(scenario = rep(scenario_n,each = 3)) %>% 
  mutate(scenario = str_replace_all(scenario,"[a-z]","")) %>%
  group_by(scenario,type) %>%
  summarise_all(mean) %>% 
  pivot_longer(
    global_GL:local_GL_tunn,
    names_to = "term",
    values_to = "value"
  ) %>%
  ggplot(aes(x = scenario, y = value, color = as.factor(type), group = as.factor(type)))+
  geom_line()+
  facet_grid(term~.)+
  theme(legend.position = "bottom")

g1 = global_local %>%
  # mutate(scenario = rep(scenario_n,each = 3)) %>% 
  mutate(scenario = str_replace_all(scenario,"[a-z]","")) %>%
  group_by(scenario,type) %>%
  summarise_all(mean) %>% 
  filter(str_detect(scenario,"120")) %>% 
  pivot_longer(
    global_GL:local_GL_tunn,
    names_to = "term",
    values_to = "value"
  ) %>%
  ggplot(aes(x = scenario, y = value, color = as.factor(type), group = as.factor(type)))+
  geom_line()+
  facet_grid(term~.)

g2 = global_local %>%
  # mutate(scenario = rep(scenario_n,each = 3)) %>% 
  mutate(scenario = str_replace_all(scenario,"[a-z]","")) %>%
  group_by(scenario,type) %>%
  summarise_all(mean) %>% 
  filter(str_detect(scenario,"200")) %>% 
  pivot_longer(
    global_GL:local_GL_tunn,
    names_to = "term",
    values_to = "value"
  ) %>%
  ggplot(aes(x = scenario, y = value, color = as.factor(type), group = as.factor(type)))+
  geom_line()+
  facet_grid(term~.)
g1/g2
```

show the contribution of global/local term
```{r}
gl_weight %>%
  # mutate(scenario = rep(scenario_n,each = 3)) %>% 
  mutate(scenario = str_replace_all(scenario,"[a-z]","")) %>%
  group_by(scenario,type) %>%
  summarise_all(mean) %>%
  pivot_longer(
    GL:GL_nbeta,
    names_to = "term",
    values_to = "value"
  ) %>%
  ggplot(aes(x = scenario, y = value, color = as.factor(type), group = as.factor(type)))+
  geom_line()+
  facet_grid(term~.)+
  theme(legend.position = "bottom")
```


```{r}
## show the comparability of Global-local term and the GL_trace

compare_gl_term = 
  global_local %>% 
  mutate(simulation = rep(1:100, each = 54)) %>% 
  group_by(simulation,scenario) %>% 
  mutate_all(function(x)(x-mean(x)))%>% 
  ungroup(simulation,scenario) %>% 
  group_by(scenario,type) %>% 
  summarise_all(mean)

compare_trace_term = 
  GL_trace %>% 
  mutate(simulation = rep(1:100, each = 54)) %>% 
  group_by(simulation,scenario) %>% 
  mutate_all(function(x)(x-mean(x))) %>% 
  ungroup(simulation,scenario) %>% 
  group_by(scenario,type) %>% 
  summarise_all(mean)

compare_gl_term
compare_trace_term
```


```{r,include=F}
## Parameter tunning
## show the relationship between silouette and nmi/rand
tunning_crit %>%
  pivot_longer(
    silourtte:rand,
    names_to = "measure",
    values_to = "value"
    ) %>%
  ggplot(aes(x = rho, y = value, color = measure, group = measure)) +
  geom_line() +
  facet_grid(measure~., scale = "free")

tunning_crit %>%
  pivot_longer(
    nmi:rand,
    names_to = "measure",
    values_to = "value"
    ) %>%
  ggplot(aes(x = silourtte, y = value, color = measure, group = measure)) +
  geom_line() +
  facet_grid(measure~., scale = "free")

  

## best rho
tunning_best %>% 
  mutate(scenario = str_replace_all(scenario,"[a-z]","")) %>%
  ggplot(aes(x = scenario,y = rho_opt)) +
  geom_boxplot()

## show the relationship between gl_trace, global_local_term and best rho
tunning_best %>% 
  group_by(scenario) %>%
  summarise_all(mean) %>%
  pivot_longer(
    gl_opt:GL_trace_opt,
    names_to = "term",
    values_to = "value"
  ) %>% 
  ggplot(aes(x = rho_opt,y = value,color = term, group = term)) +
  geom_line()+
  facet_grid(term~., scale = "free")
```





# 2 simulation result comparison

```{r}
eva_nmi = NULL
eva_rand = NULL
gl_weight = NULL
global_local = NULL
GL_trace = NULL
tunning_crit = NULL
gl_weight = NULL
tunning_best = NULL
files = list.files("./data/simu_1229/")
for(i in 1:length(files)){
  load(file = paste("./data/simu_1229/", files[i], sep = ""))
  eva_nmi = rbind(eva_nmi,res$eva_nmi)
  eva_rand = rbind(eva_rand, res$eva_rand)
  gl_weight = rbind(gl_weight, res$gl_weight)
}
```

## nmi comparison

```{r}
nmi_mean = eva_nmi %>% 
  group_by(scenario) %>% 
  summarise_all(mean) %>% 
  separate(scenario,into = c("ratio","eff","sigma","div"), sep = "_")


nmi_balanced_div2 = nmi_mean %>% 
  filter(ratio == "sub1111"&div == "div2") %>% 
  dplyr::select(eff, sigma,concatenation = nmi_spec_c, SNF = nmi_spec_s, absnf = nmi_spec_abs, gl = nmi_spec_g2, gl_nogl = nmi_spec_g2_nogl) %>% 
  pivot_longer(
    concatenation:gl_nogl,
    names_to = "methods",
    values_to = "nmi"
  ) %>% 
  # filter(str_detect(methods, "gl")) %>% 
  ggplot(aes(x = eff, y = nmi, color = methods, group = methods))+
  geom_line()+
  geom_point()+
  facet_grid(sigma~.)+
  theme(legend.position = "bottom")+
  ggtitle("balanced_div2")

nmi_balanced_div4 = nmi_mean %>% 
  filter(ratio == "sub1111"&div == "div4") %>% 
  dplyr::select(eff, sigma,concatenation = nmi_spec_c, SNF = nmi_spec_s, absnf = nmi_spec_abs, gl = nmi_spec_g2, gl_nogl = nmi_spec_g2_nogl) %>% 
  pivot_longer(
    concatenation:gl_nogl,
    names_to = "methods",
    values_to = "nmi"
  ) %>% 
  # filter(str_detect(methods, "gl")) %>% 
  ggplot(aes(x = eff, y = nmi, color = methods, group = methods))+
  geom_line()+
  geom_point()+
  facet_grid(sigma~.)+
  theme(legend.position = "bottom")+
  ggtitle("balanced_div4")
library(patchwork)
nmi_balanced_div2+nmi_balanced_div4
library(plotly)
ggplotly(p = nmi_balanced_div2)
ggplotly(p = nmi_balanced_div4)
```

## weight comparison

```{r}
weight_2methods = as_tibble(gl_weight) %>% 
  separate(scenario,into = c("ratio","eff","sigma","div"), sep = "_") %>%
  filter(ratio == "sub1111"&div == "div4") %>%
  dplyr::select(eff,sigma,type,gl = GL2, gl_nogl = GL2_nogl) %>% 
  pivot_longer(
    gl:gl_nogl,
    names_to = "methods",
    values_to = "weights"
  ) %>% 
  ggplot(aes(x = factor(type), y = weights, color = methods))+
  geom_boxplot()+
  facet_grid(eff~sigma)

weight_gl = as_tibble(gl_weight) %>% 
  separate(scenario,into = c("ratio","eff","sigma","div"), sep = "_") %>%
  filter(ratio == "sub1111"&div == "div4") %>%
  dplyr::select(eff,sigma,type,weights = GL2) %>% 
  ggplot(aes(x = factor(type), y = weights))+
  geom_boxplot(color = "red")+
  facet_grid(eff~sigma)+
  ggtitle("gl_weights")

weight_glno = as_tibble(gl_weight) %>% 
  separate(scenario,into = c("ratio","eff","sigma","div"), sep = "_") %>%
  filter(ratio == "sub1111"&div == "div4") %>%
  dplyr::select(eff,sigma,type,weights = GL2_nogl) %>% 
  ggplot(aes(x = factor(type), y = weights))+
  geom_boxplot(color = "blue")+
  facet_grid(eff~sigma)+
  ggtitle("gl_nogl_weights")
  
weight_glno+weight_gl
```







