---
title: "trivial_analysis"
author: "yuqimiao"
date: "2020-09-08"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---

# For cluster evaluation index
```{r}
library(igraph)
library(tidyverse)
compare(rep(1:3,times = c(15,15,120)),rep(1:2, times = c(30,120)),method = "nmi")
compare(rep(1:3,times = c(15,15,120)),rep(1:2, times = c(30,120)),method = "rand")
```

It can be seen that, using the rand and nmi as evaluation criterion, although A/B can't be divide, the index is also very high

# simulation logic

1. here we are assuming every data can only provide 1 division, which means for a type of data, we can only cluster to 2 subtypes;
2. For this simulation setting, we can also expand our subtype number to 5 or 6, which can be divided by:

for 5
  * "12/345"
  * "13/245"
  * "14/235"

for 6
  * 123/456
  * 145/236
  * 124/356

(use plot to show the division)

we can directly change the sub_ratio, data_division to get 5 or 6 subtype
```{r}
# try using 4 groups divided by 3 types of data

## input
size = 240
sub_ratio = c(rep(0.2,4),rep(0.1,2))
eff_size = rep(5,3)
sigma = 10
data_divide ="123/456"
dist = "normal"

## calculate index_cut for given subtype ratio
index_cut = cumsum(sub_ratio)*size
index = list()
for(i in 1:length(index_cut)){
  if(i == 1){
    index[[i]] = 1:index_cut[1]
  }else{
    index[[i]] = (index_cut[[i-1]]+1):index_cut[[i]]
  }
}

### for a data
data1 = matrix(0,size, 1000)
divide = lapply(X = str_split(str_split(data_divide,pattern = "/")[[1]], pattern = ""), 
                FUN = as.numeric
                )
ind1 = NULL
for(i in 1:length(divide[[1]])){
  ind1 = c(ind1, index[[divide[[1]][i]]])
}
ind2 = NULL
for(i in 1:length(divide[[2]])){
  ind2 = c(ind2, index[[divide[[2]][i]]])
}
if (dist == "normal"){
  data1[ind1,1:50] = rnorm(length(ind1)*50, eff_size[1], sqrt(sigma))
  data1[ind2,1:50] = rnorm(length(ind2)*50, -eff_size[1], sqrt(sigma))
}else if(dist == "logit"){
  data1[ind1,1:50] = sapply(X = rnorm(length(ind1)*50, eff_size[1], sqrt(sigma)),
                            FUN = function(x) exp(x)/(1+exp(x))
                            )
  data1[ind2,1:50] = sapply(X = rnorm(length(ind2)*50, -eff_size[1], sqrt(sigma)),
                            FUN = function(x) exp(x)/(1+exp(x))
                            )
}

truelabel = NULL
  for (i in 1:length(index)){
    truelabel = c(truelabel, rep(i,length(index[[i]])))
  }
par(mfrow = c(2,1))
hist(data1[1:144,1:50], main = "the first 3 subtype")
hist(data1[145:200,1:50], main = " the latter 3 subtype")
```
3. For weight construction

Using the best performance setting for abSNF( from peifeng's paper)
```{r}
n1 = 50*0.6#n1 is # of correct weights for informative features
n2 = 950*0.8#n2 is # of correct weights for non-informative features
r1 = 1
r2 = 3
uninfo_r1 = 0
uninfo_r2 = 1
#r1, r2, uninfo_r1, uninfo_r2 define the magnitude of correct wights 
ge_weight=abs(runif(1000,0,1))
s=sample(1:50,n1)
ge_weight[s]=runif(n1,r1,r2)
ss=sample(51:1000,n2)
ge_weight[ss]=runif(n2,uninfo_r1,uninfo_r2)
plot(1:1000, ge_weight)
```

# Steps for a single data:

From every data type, we want to get the result:

1. multiple kernels
2. affinity matrix
3. eigen gap result
4. SIMLR result

Firstly, for clarification, the affinity matrix gives the RBF kernels of the data, while the multiple kernel getting from SIMLR-multiple.kernel function gives the nomalized distance btw subjects, so we can't just using the averaged multiple kernel to do the SNF

```{r}
# check affinity matrix and kernels
library(abSNF)
library(SIMLR)
library(SNFtool)
library(parallel)
library(Matrix)
source("./code/R/compute.multiple.kernel.R")
data1 = standardNormalization(data1)
mk1 = multiple.kernel(data1)
af1 = affinityMatrix(dist2_w(as.matrix(data1),as.matrix(data1), weight = ge_weight))
par(mfrow = c(2,1))
displayClusters(af1, truelabel)
displayClusters(as.matrix(mk1[[1]]), truelabel)
```

## gap and SIMLR results 
```{r}
K = 2
cores.ratio = 0.5
gap1 = estimateNumberOfClustersGivenGraph(af1,2:5)$`Eigen-gap best`
simlr1 = SIMLR(t(data1), K,cores.ratio = cores.ratio)
nmi = compare(simlr1$y$cluster,truelabel, method = "nmi")
rand = compare(simlr1$y$cluster,truelabel, method = "rand")
nmi
rand
```




















